---
title: "Geomatics for Kaggle Sberbank Russian Housing Market competitions"
output:
  html_notebook:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    theme: yeti
    toc: yes
  html_document:
    fig_height: 5
    fig_width: 8
---

# The competition

The competition : [Sberbank Russian Housing Market](https://www.kaggle.com/c/sberbank-russian-housing-market)  
Can you predict realty price fluctuations in Russia’s volatile economy?  


```{r, include=FALSE}
# PACKAGE LOADING
library(dplyr)
library(sp)
library(rgdal)
library(leaflet)
library(data.table)
library(DT)


addTiles = function (map, urlTemplate = "http://{s}.tile.openstreetmap.org/{z}/{x}/{y}.png",
attribution = NULL, layerId = NULL, group = NULL, options = tileOptions())
{
options$attribution = attribution
if (missing(urlTemplate) && is.null(options$attribution))
options$attribution = paste("© OpenStreetMap",
"contributors, CC-BY-SA")
invokeMethod(map, getMapData(map), "addTiles", urlTemplate,
layerId, group, options)
}
```

# SHAPEFILE and data

The shapefile data has been found here: [http://gis-lab.info/qa/moscow-atd.html](http://gis-lab.info/qa/moscow-atd.html).  
(This is the second **ESRI shape** file)

```{r}
mo_shp <- readOGR(dsn = "shp_mo", layer = "mo", stringsAsFactors = FALSE)
plot(mo_shp)
```

We also need the train dataset from Kaggle:
```{r}
# KAGGLE DATA FILE
train_df <- fread("../input/train.csv", stringsAsFactors = FALSE)
# test_df <- fread("input/test.csv", stringsAsFactors = FALSE)
```

```{r}
length(unique(train_df$sub_area))
```

The federal city of Moscow, Russia is divided into twelve administrative okrugs, which are in turn subdivided into districts (raions). [(source Wikipedia)](https://en.wikipedia.org/wiki/Administrative_divisions_of_Moscow)  
There are 146 raions, which are the **146 different sub_area**, which are the **NAME** of the shapefile.

The only issue is that the raion names don't match. Those from Kaggle (**sub_area**) are in English while those on the shapefile (**NAME**) are in Russian.  
For information: The other variable **OKRUGS** matches with **ABBREV_AO**. There are the 12 administrative okrugs.


I have created a dictionnary which matches everything. 

```{r, echo=TRUE}
NAME_to_subarea <- read.csv("NAME_to_subarea.csv", stringsAsFactors = FALSE)
head(NAME_to_subarea)
```

Then we only need to merge the new columns.

```{r}
mo <- merge(mo_shp, NAME_to_subarea)
modata <- mo@data;modata
```

# Plot the shapefile
```{r}
factpal <- colorFactor(topo.colors(12), mo@data$OKRUG)

labels <- sprintf(
  "<strong>%s</strong><br/>AO: %s",
  mo@data$sub_area, mo@data$OKRUG
) %>% lapply(htmltools::HTML)


OKRUGS <- leaflet(mo) %>% 
  addTiles() %>%
  addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.5,
              fillColor = ~factpal(OKRUG),
              highlightOptions = highlightOptions(color = "white", weight = 2,
                                                  bringToFront = TRUE),
              label = labels,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  addLegend(pal = factpal, values = ~OKRUG, opacity = 1)
OKRUGS
```

# Plot some useful data {.tabset}

We want now to plot the price of the transactions.

```{r}
data <- train_df %>%
  filter(full_sq > 0) %>%
  mutate(price_sq = price_doc/full_sq) %>%
  group_by(sub_area) %>%
  summarise(nb = n(),
            mean_price_doc = mean(price_doc),
            mean_price_sq = mean(price_sq))

mo <- merge(mo, data)
```

```{r}
pal1 <- colorNumeric(
  palette = "YlOrRd",
  domain = mo@data$mean_price_doc)

pal2 <- colorNumeric(
  palette = "YlOrRd",
  domain = mo@data$mean_price_sq)

labels <- sprintf(
  "<strong>%s</strong><br/>AO: %s. <br/>Mean sale price: %g. <br/>Square metre cost: %g. <br/>Number of transactions: %g",
  mo@data$sub_area, mo@data$OKRUG, mo@data$mean_price_doc, mo@data$mean_price_sq, mo@data$nb
) %>% lapply(htmltools::HTML)

```

## Square meter cost

```{r}
map1 <- leaflet(mo) %>% 
  addTiles() %>%
  addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.5,
              fillColor = ~pal1(mean_price_doc),
              highlightOptions = highlightOptions(color = "white", weight = 2,
                                                  bringToFront = TRUE),
              label = labels,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  addLegend(pal = pal1, values = ~mean_price_doc, opacity = 1, title = "Average selling prices")
map1
```

## Mean price sale 

```{r}
map2 <- leaflet(mo) %>% 
  addTiles() %>%
  addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.5,
              fillColor = ~pal2(mean_price_sq),
              highlightOptions = highlightOptions(color = "white", weight = 2,
                                                  bringToFront = TRUE),
              label = labels,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  addLegend(pal = pal2, values = ~mean_price_sq, opacity = 1, title = "Average selling prices")
map2
```


